Broom: Safe Region-Based Memory Management for Dataflow Programs

### 2015-10-22 paper/type-system.tex
Sec 3 complete.

>>>>

To help state the type safety theorem, we define the syntactic class
of values in \FB as following:
\begin{smathpar}
\begin{array}{lclcl}
v & \in & \mathtt{values} & \coloneqq & \C{new}\; cn\inang{\tbar}
      \inang{\ralloc\rbar} \ALT \invalidexn \\
\end{array}
\end{smathpar}
Type safety theorem is stated thus:
\begin{theorem}
\emph{(\textbf{Type Safety})}
\label{thm:core-safety}
Let $\A_{\emptyset} = (\emptyset,\cdot,true)$ denote an empty context.
If $\hastyp{\A_{\emptyset}, \toprgn, \cdot}{e}{\tau}$, then either $e$
is a value, or there exists an $e'$ such that $e \redsto
e'$ and $\hastyp{\A_{\emptyset}, \toprgn, \cdot}{e'}{\tau}$.
\end{theorem}
